Emittance preservation of an electron bunch in a loaded quasi-linear plasma wakefield

### 2017-07-11 Tex/Paper.tex
Added some figures, and addes SVG support in makefile

\documentclass[aps,prstab,reprint,amsmath,amssymb,groupedaddress]{revtex4-1}
\bibliographystyle{apsrev4-1}
\usepackage{hyperref}
\hypersetup{colorlinks=true, citecolor=blue, urlcolor=blue, linkcolor=blue}

@@

Earlier simulations with witness beam $\sigma_{r} = 100\unit{\mu m}$ causes the beam radius to rapidly shrink as the
beam enters the plasma \cite{berglyd_olsen:2016}. This is due to a mismatch between beam emittance and the plasma
density. The relation is given by
\begin{align}
    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_p}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
\end{align}
where $\lambda_{p}$ is the plasma wavelength.

@@

%~ - describe proton beam wake structure [similar to that of a modulated proton beam] (simulation results to show:
%~   unloaded wake)
The structure of the single drive beam setup behaves similarly to the self-modulated case. However, since the drive
beam is prevented from significant evolution in this simulation setup, we are presented with an idealised case where
the electron witness beam sees consistent fields.

@@

>>>>

\documentclass[aps,prstab,reprint,amsmath,amssymb,groupedaddress]{revtex4-1}
\bibliographystyle{apsrev4-1}

\usepackage{hyperref}
\hypersetup{colorlinks=true, citecolor=blue, urlcolor=blue, linkcolor=blue}

\usepackage{graphicx}

@@

Earlier simulations with witness beam $\sigma_{r} = 100\unit{\mu m}$ causes the beam radius to rapidly shrink as the
beam enters the plasma \cite{berglyd_olsen:2016}. This is due to a mismatch between beam emittance and the plasma
density. The relation is given by
\begin{align}
    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_p}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
\end{align}
where $\lambda_{p}$ is the plasma wavelength. In these simulations we have used matched beams for emittances between
$2$ and $6\unit{\mu m}$.

@@

%~ - describe proton beam wake structure [similar to that of a modulated proton beam] (simulation results to show:
%~   unloaded wake)

The structure of the single drive beam setup behaves similarly to the self-modulated case. However, since the drive
beam is prevented from significant evolution in this simulation setup, we are presented with an idealised case where
the electron witness beam sees consistent fields.

\begin{figure}
    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/beamLoading}
    \label{Fig:BeamLoading}
    \caption{Comparison between the unloaded longitudinal e-field (no witness beam) and the loaded e-field along the
        axis. The magnitude of the beam density along the axis is shown for reference. The beams travel towards the
        left. $\xi = z - tc$ is the position in the simulation box. The beam density is in units of plasma density
        $n_{0} = 7\nexp{-14}\unit{cm}^{-3}$.}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/plasmaDenTWake}
    \label{Fig:PlasmaDenTWake}
    \caption{}
\end{figure}
